Supplementary material

### 2024-09-05 output/Main_text.Rmd
Reorders main output files
Main output files are moved to the main output folder, instead of a subfolder

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that Multidimensional Item Response Theory
  accurately represents covariate spaces with correlated dimensions and/or
  non-standard variances. As it is also used in applications in the
  non-cognitive domain, they also need to model negatively-keyed items
  accurately and interpretably. Henceforth we generalize the
  multidimensional discrimination [@reckase_discriminating_1991] and
  difficulty [@reckase_difficulty_1985] parameters to account for those two
  phenomena. We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. This results in three different versions of
  the multidimensional parameters: The original one, based on the item
  parameters solely, one that incorporates the covariance structure of the
  latent space, and a third one that uses the correlation structure instead.
  Following @ackerman_creating_1994, we also provide a geometrical
  representation based on these parameters, and provide applied examples to
  illustrate the pertinence of these generalized parameters to represent the
  measurement properties of the items accurately. We recommend using the
  version that uses the latent covariance structure for describing the
  properties of the parameters, and the one based on the correlation structure
  for graphical representation. Finally, we discuss the implications of this
  generalization for other multidimensional IRT models, and the parallels of our
  results in common factor model theory.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../../www/Multidimensional-parameters-MCLM.bib, ../../www/packages.bib]
csl:          ../../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

```{r write-bib}
#| cache: true

# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```

>>>>

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that Multidimensional Item Response Theory
  accurately represents covariate spaces with correlated dimensions and/or
  non-standard variances. As it is also used in applications in the
  non-cognitive domain, they also need to model negatively-keyed items
  accurately and interpretably. Henceforth we generalize the
  multidimensional discrimination [@reckase_discriminating_1991] and
  difficulty [@reckase_difficulty_1985] parameters to account for those two
  phenomena. We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. This results in three different versions of
  parameters solely, one that incorporates the covariance structure of the
  latent space, and a third one that uses the correlation structure instead.
  Following @ackerman_creating_1994, we also provide a geometrical
  representation based on these parameters, and provide applied examples to
  illustrate the pertinence of these generalized parameters to represent the
  measurement properties of the items accurately. We recommend using the
  version that uses the latent covariance structure for describing the
  properties of the parameters, and the one based on the correlation structure
  for graphical representation. Finally, we discuss the implications of this
  generalization for other multidimensional IRT models, and the parallels of our
  results in common factor model theory.
  the multidimensional parameters: The original one, based on the item
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

@@

```{r write-bib}
# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```

### 2024-09-05 output/Supplementary_material.Rmd
Reorders main output files
Main output files are moved to the main output folder, instead of a subfolder

---
title: "Supplementary material"
output:
  officedown::rdocx_document:
    tables:
      caption:
        pre: "Table S."
      style: APA_Like_style
    mapstyles:
      Body Text: First Paragraph
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
bibliography: [../../www/Multidimensional-parameters-MCLM.bib, ../../www/packages.bib]
csl:          ../../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Supplementary material"
output:
  officedown::rdocx_document:
    tables:
      caption:
        pre: "Table S."
      style: APA_Like_style
    mapstyles:
      Body Text: First Paragraph
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---
